Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-13 MSc-dissertation.tex
Skeleton added

@@

@@

\subsection{Hard bits}
You might want to include an equation here:

\begin{equation} \delta N_{\nu} = (\delta N_{\nu})_{ex} + (\delta N_{\nu})_{au} 
\label{equation:delsplit}
% note that the label is optional but allows you to refer to this
% equation later.
\end{equation}

\subsection{Even harder bits}
This might be one of the places where you might want to refer to
equation \ref{equation:delsplit}. You will usually need to use the
Latex command twice to make cross-references like this work properly.
The cross-reference information is stored in the {\em .aux} file so don't
delete it.

\subsubsection{Numbering}
You can keep subdividing but eventually you get to a level where
numbering stops. This text is in a subsubsection which is not numbered
by default.

\paragraph{More on numbering:}

This text is in a paragraph which is also not numbered by default and
the ``title'' of the paragraph is not on a separate line.
If you want to increase the depth to which sections are numbered you
should see the section on setting the secnumdepth counter in the manual.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

HOW PYABC parallelise the sampling

@@

The program is executed on Cirrus, using 8, 12, 16, 24, 36, 54, 72 cores respectively. Each run is repeated 5 times. The average execution time, required sampling numbers are recorded. Hyperthreading is enabled when using 54 and 72 cores. The access to the node that contains computation cores is exclusive, such that the execution would not be affected by other programs of operations.

@@

@@

@@

@@

@@

@@

>>>>

[background and motivation]

[what is done]

@@

[describe the process and how cells and cytokines are involved]

@@

[how this can be modelled as dynamic systems]

[general topics of mathematical models: how to build model according to interactions; how to calibrate/ parameterise the model; how to solve the model; dynamics; how to evaluate the model]

@@

[how to parameterise the model]

[how the infer the parameter given data]

[likelihood-free inference and information about ABC SMC]

[model comparison, ABC SMC for model comparison]

@@

[existing tools and software for this task]

[workflow and developing]

@@

[feasible or not; goodness of fit; features of these models]

[bayes factor for model selection]

@@

[hypothesis]

[available data]

[model misspecification]

@@

[implementation details and options/ settings that are affecting the ABC]

@@

[including the options that are tested/ tried/ not adopted]

[how do these options correspond to biological model and how to set them accordingly for proposed model]

[experiments plan]

@@

[ABC implementations details, e.g. distance, population, ODE related functions]

@@

[comparison of model 1, 2 and 3]

[further comparison of model 3, 4 and 5]

@@

[MORE meanings of the performance study]

@@

[HOW PYABC parallelise the sampling]

@@

The program is executed on Cirrus, using 8, 12, 16, 24, 36, 54 and 72 cores respectively. Each run is repeated 5 times. The average execution time, required sampling numbers are recorded. Hyperthreading is enabled when using 54 and 72 cores. The access to the node that contains computation cores is exclusive, such that the execution would not be affected by other programs of operations.

@@

[WHAT results is outputted and WHAT topics are discussed]

@@

[inferred parameters: joint distribution, estimated values and simulated trajectory for each models; sensitivity; features of the inferred model]

[model selections result; bayes factor]

@@

[scaling-up performance: speed-up and efficiency]

[profiling results: hot-spot and possible improvements]

@@

[goodness of fit (evaluation); preferred models and effects of modification to basic model]

[efficiency and trade-offs in scaling-up]

[POSSIBLE: compare to exact inference; compared to other implementations]

[limitations]

@@

[something not done as scheduled]

[interesting topics to look inside]

[moving to generalisations]

@@

[what is studied]

[to what extend]

[how good is the result]

[summary of the findings and advise]

[thanks]
